---
title: "Evaluations of positive and negative stimuli using the Affective Misattribution Procedure (AMP) and self-reports"
subtitle: "Data processing"
author: "Template: Ian Hussey; content: [FlorianStucki]"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    code_folding: hide
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

```{r, include=FALSE}

knitr::opts_chunk$set(message = FALSE,
                      warning = FALSE)

```

# Dependencies

```{r}

library(dplyr)
library(tidyr)
library(readr)
library(janitor) # for clean_names()
library(stringr)

```

# Get data

```{r}

# demographics
data_demographics_raw_messy <- read_csv("../data/raw/data_demographics_raw_messy.csv", skip = 2) |>
  janitor::clean_names()

data_demographics_raw <- read_csv("../data/raw/data_demographics_raw.csv") |>
  janitor::clean_names()

# self report measure
data_selfreport_raw <- read_csv("../data/raw/data_selfreport_raw.csv") |>
  janitor::clean_names()

# affect attribution procedure
data_amp_raw <- read_csv("../data/raw/data_amp_raw.csv") |>
  janitor::clean_names()

```

# Demographics

Clean the demographics data so that summaries of age and gender can be made in the analysis.

```{r}
#filter= row, select = spalten
#Daten in einem neuen Datensatz aufbereiten und umbennen
colnames(dat_age_gender)
dat_age_gender <- data_demographics_raw |> 
  select(subject, trialcode, response) |> #select columne
  rename(unique_id= subject, item = trialcode)|>
  filter(item == "age") |>  #filter row
  mutate(response = str_remove_all(response,"\\D"), 
        response = na_if(response,""),
        response = as.numeric(response)) #alle nicht nummerischen vektoren entfernen
  

temp <- dat_age_gender |> distinct(responseNA_real_temp <- dat_age_gender |> distinct(response) #übersicht für die verschiedenen Antworten
sapply(dat_age_gender,class) #welche klassen haben die columes


```
```{r}
#Extract Gender from the Raw Data
dat_Gender <- data_demographics_raw |> 
  select(subject, trialcode, response) |> #select column
  rename(unique_id= subject, item = trialcode) #rename column
  

Dat_long_complete <- pivot_wider(dat_Gender,names_from = "item", values_from = "response") |> #separate age/gender column
  group_by(unique_id) |> #delete duplicate entries
  reframe(age = first(age),gender=first(gender)) |> 
  distinct(unique_id, .keep_all = TRUE) |> 
  mutate(gender = case_when( #mutate gender to F, M and NB. Mark other entries as NA.
    tolower(gender) == "female" ~ "F",
    tolower(gender)== "woman" ~ "F",
    tolower(gender) == "male" ~ "M",
    tolower(gender) == "non binary" | tolower(gender) == "non-binary" ~ "NB",
    TRUE ~ NA)) |>  
  mutate(age = str_remove_all(age,"\\D"), #mark other entries than a Number as NA
        age = na_if(age,""),
        age = as.numeric(age)) #Mutate the age column as numeric
    
```


# Exclusions / data quality

## AMP

Create an exclusion variable `exclude_amp_performance` based on AMP performance: "exclude" if more than 10% of trials are < 100ms, or "include" if not.

Create an exclusion variable `exclude_amp_completeness` based on the AMP having the right number of trials.

```{r}

#data_amp_performance_criteria <- data_amp_raw 



```

# Self-reports

Create a mean score for each participant of the three self-report items.

```{r}

#data_selfreport_trial_level <- data_selfreport_raw 

```

# Affect Misattribution Procedure

Create an overall AMP bias score. Score each trial as having been evalauted as congruent with the prime or not. eg When trialcode == "prime_positive" & evaluative_response == 1, then record as 1, etc. AMP score is the proportion of congruent responses.

```{r}

#data_amp_score_congruence <- data_amp_raw 

```

# Combine 

Combine data frames together to create one wide-format data frame where each row represents a participant.

Flag all duplicates for exclusion.

```{r}

# data_processed_before_exclusions 

```

# Define master exclusion variable

```{r}

#data_processed <- data_processed_before_exclusions

```

# Write to disk

```{r}

# # in case this dir doesn't exist, create it
# dir.create("../data/processed/")
# 
# # save data to disk in that dir
# write_csv(data_processed, "../data/processed/data_processed.csv")

```

# Session info

```{r}

sessionInfo()

```


